Methodological Details - Blue Bananas

### 2021-01-18 docs/ExperimentalDetails/Experimental_details.Rmd
:art: - use numbered sections + appendix
use expex

---
title: "Methodological Details - Blue Bananas"
author: ""
date: "9/17/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)

## 1. Research Questions

@@

## 2. Participants

@@

## 3. Procedure

@@

\noindent “Du sollst den Würfel auf der grünen Sonnenbrille ablegen.”  
\noindent *engl. 'You have to put the cube on top of the green sunglasses.'*

@@

\noindent “Und jetzt sollst du den Würfel auf der grünen Avokado ablegen.”  
\noindent *engl. 'And now, you have to put the cube on top of the green avocado.'*

@@

## Additional Information {#adds}

@@

### A.1 Selection of stimuli superset

@@

### A.2 The norming study

@@

### A.3 Selection of experimental stimuli

@@

## A.4 Randomization

>>>>

---
title: "Methodological Details - Blue Bananas"
author: ""
date: "9/17/2020"
output:
  pdf_document:
    number_sections: true
    keep_tex: true
header-includes:
  - \usepackage{expex}
  - \lingset{everygla=,everyglpreamble=\it}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "tbp")
options(tinytex.verbose = TRUE)
```

# Research Questions

@@

# Participants

@@

# Procedure

@@

```{=latex}
\ex \begingl
\glpreamble Du sollst den Würfel auf der grünen Sonnenbrille ablegen.//
\gla du sollst den würfel auf der grünen sonnenbrille ablegen.//
\glb you have.to the cube on the green sunglasses put//
\glft `You have to put the cube on top of the green sunglasses.'//
\endgl \xe
```

@@

```{=latex}
\ex \begingl
\glpreamble Und jetzt sollst du den Würfel auf der grünen Avokado ablegen.//
\gla und jetzt sollst du den würfel auf der grünen avokado ablegen//
\glb and now have.to you the cube on the green avocado put//
\glft `And now, you have to put the cube on top of the green avocado.'//
\endgl \xe
```

@@

\appendix

# Additional Information {#adds}

@@

## Selection of stimuli superset

@@

## The norming study

@@

## Selection of experimental stimuli

@@

# Randomization
